\LARGE \bf Mean Estimation from One-Bit Measurements

### 2022-04-27 ak-bio.tex
addressed specific commets in R2
updated bios

Alon Kipnis is a Senior Lecturer at the Efi Arazi School of Computer Science at Reichman University. Preivously, he was a postdoctoral research scholar and a lecturer at the Department of Statistics at Stanford University, advised by David Donoho. He completed the Ph.D. in electrical engineering from Stanford University in 2017. Dr. Kipnis is the recipient of numerous fellowships and awards, including the Koret foundation postdoctoral fellowship, Stanford's electrical engineering department fellowship, and a prize from the Wolf Foundation. His research is in the areas of mathematical statistics and information theory.

>>>>

Alon Kipnis is a Senior Lecturer (Assistant Professor) at the School of Computer Science at Reichman University. Previously, he was a postdoctoral research scholar at the Department of Statistics at Stanford University, advised by David Donoho. He completed his Ph.D. in electrical engineering from Stanford University in 2017. His research is in the areas of mathematical statistics and information theory. He is particularly interested in ambitious machine learning and data science applications of his theoretical work.

Dr. Kipnis is the recipient of numerous fellowships and awards, including the Koret foundation postdoctoral fellowship, Stanford's electrical engineering department fellowship, and a prize from the Wolf Foundation. His research is in the areas of mathematical statistics and information theory.

### 2022-04-27 problem-formulation.tex
ready for submission
addressed specific commets in R2
updated bios

We measure the performance of an estimator $\theta_n \defeq
\theta_n(B_1^n)$ by one of a few notions. In the simplest case,
we assume a prior $\pi$ on $\theta$ (which may be a point
mass) and consider the quadratic risk
\begin{equation}
  \label{eq:error_def}
  R_n = R_n(\pi) \defeq \int \E_\theta\left({\theta}_n - \theta \right)^2
  d\pi(\theta),
\end{equation}
where the expectation is taken with respect to the distribution of
$X_1,\ldots,X_n \simiid P_\theta$.  The main problems we consider in this
paper are the minimal value of the risk~\eqref{eq:error_def} as a function
of the sample size $n$ and the density $f$, under different choices of the
encoding functions in
cases~\eqref{item:centralized}--\eqref{item:distributed}.
The quadratic risk~\eqref{eq:error_def} may be infinite in some cases;
we defer discussion of this case to later sections, as it is technically
demanding and detracts from the presentation here.

@@

To describe our results and make them formal, we require some additional
notation and one main assumption, which restricts the class of distributions
we consider.  We use the typical notation that
$F(x) = \int_{-\infty}^x f(t) dt$ is the cumulative distribution function
of the $X_i$, and we let
\begin{equation*}
  h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
\end{equation*}
be the \emph{hazard} function (or the \emph{failure rate} or \emph{force of
  mortality}), which is monotone increasing as $f$ is
log-concave~\cite{bagnoli2005log}. Given the centrality of the median
to our efficiency bounds, it is unsurprising that the quantity
\begin{equation}
  \label{eq:eta_def}
  \eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))}
  \stackrel{(\star)}{=} \frac{f(x)f(-x)}{F(x)F(-x)}
\end{equation}
appears throughout our development. (Here equality~$(\star)$ is immediate by
the symmetry of $f$.)  For $p \in (0, 1)$ and $x = F^{-1}(p)$,
\begin{equation}
  \label{eqn:variance-quantiles}
  \frac{1}{\eta(x)} =
  \frac{1}{\eta(F^{-1}(p))}
  = \frac{p (1 - p)}{f(F^{-1}(p))^2}
\end{equation}
is of course the familiar asymptotic variance of the $p$th quantile of the sample $X_1,\ldots,X^n$ (cf.~\cite{VanDerVaart98}, Ch.~21).

>>>>

We measure the performance of an estimator $\theta_n \defeq
\theta_n(B_1,\ldots,B_n)$ by one of a few notions. In the simplest case,
we assume a prior $\pi$ on $\theta$ (which may be a point
mass) and consider the quadratic risk
\begin{equation}
  \label{eq:error_def}
  R_n = R_n(\pi) \defeq \int \E_\theta\left({\theta}_n - \theta \right)^2
  d\pi(\theta),
\end{equation}
where the expectation is taken with respect to the distribution of
$X_1,\ldots,X_n \simiid P_\theta$.  The main problems we consider in this
paper are the minimal value of the risk~\eqref{eq:error_def} as a function
of the sample size $n$ and the density $f$, under different choices of the
encoding functions in
cases~\eqref{item:centralized}--\eqref{item:distributed}.
The quadratic risk~\eqref{eq:error_def} may be infinite in some cases;
we defer discussion of this case to later sections, as it is technically
demanding and detracts from the presentation here.

@@

To describe our results and make them formal, we require some additional
notation and one main assumption, which restricts the class of distributions
we consider.  We use the typical notation that
$F(x) = \int_{-\infty}^x f(t) dt$ is the cumulative distribution function
of the $X_i$, and we let
\begin{equation*}
  h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
\end{equation*}
be the \emph{hazard} function (or the \emph{failure rate} or \emph{force of
  mortality}), which is monotone increasing as $f$ is
log-concave~\cite{bagnoli2005log}. Given the centrality of the median
to our efficiency bounds, it is unsurprising that the quantity
\begin{equation}
  \label{eq:eta_def}
  \eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))}
  \stackrel{(\star)}{=} \frac{f(x)f(-x)}{F(x)F(-x)}
\end{equation}
appears throughout our development (equality~$(\star)$ is immediate by
the symmetry of $f$). For $p \in (0, 1)$ and $x = F^{-1}(p)$,
\begin{equation}
  \label{eqn:variance-quantiles}
  \frac{1}{\eta(x)} =
  \frac{1}{\eta(F^{-1}(p))}
  = \frac{p (1 - p)}{f(F^{-1}(p))^2}
\end{equation}
is of course the familiar asymptotic variance of the $p$th quantile of the sample $X_1,\ldots,X_n$ (cf.~\cite{VanDerVaart98}, Ch.~21).
